% Appendix B: Reuse Summary — MANDATORY (Handbook 9.6)
% Must always be Appendix B.
\section{Reuse Summary}
\label{app:reuse}

This appendix documents all third-party software reused in this project, as required by the handbook.

\subsection*{Frameworks and Libraries}

\begin{table}[H]
\centering
\begin{tabular}{llll}
\toprule
\textbf{Component} & \textbf{Version} & \textbf{Licence} & \textbf{Usage} \\
\midrule
veilid-core    & (local build)  & MPL-2.0        & P2P networking, DHT, private routing \\
MP-SPDZ        & (local build)  & BSD-3-Clause   & MASCOT MPC protocol execution \\
Dioxus          & 0.7.2          & MIT/Apache-2.0 & Desktop UI framework \\
tokio           & 1.x            & MIT            & Async runtime \\
serde           & 1.0            & MIT/Apache-2.0 & Serialization framework \\
ciborium        & 0.2            & MIT/Apache-2.0 & CBOR serialization for DHT records \\
bincode         & 1.3            & MIT            & Binary serialization for messages \\
sha2            & 0.10           & MIT/Apache-2.0 & SHA-256 hashing (bid commitments) \\
aes-gcm         & 0.10           & MIT/Apache-2.0 & AES-256-GCM content encryption \\
rand            & 0.8            & MIT/Apache-2.0 & Random number generation \\
anyhow          & 1.0            & MIT/Apache-2.0 & Error handling \\
thiserror       & 1.0            & MIT/Apache-2.0 & Error type derivation \\
tracing         & 0.1            & MIT            & Structured logging \\
async-trait     & 0.1            & MIT/Apache-2.0 & Async trait support \\
\bottomrule
\end{tabular}
\caption{Third-party libraries used in the Lattice crate.}
\label{tab:reuse}
\end{table}

\subsection*{Development Tools}

\begin{itemize}[noitemsep]
  \item \textbf{Docker devnet}: Initial devnet environment adapted from a Veilid community merge request~\cite{veilid-devnet-mr444}; later replaced by the Veilid Playground (process-based, no Docker).
  \item \textbf{cargo-nextest}: Test runner for parallel and sequential test execution.
  \item \textbf{libipspoof.so}: LD\_PRELOAD library from Veilid devcontainer for IP address spoofing in devnet. Source: Veilid repository (MPL-2.0).
\end{itemize}

\subsection*{Code Reuse from Reference Applications}

The Veilid project's \texttt{veilidchat} application was studied as a reference for Veilid API usage patterns (DHT record creation, routing context setup, message handling). No code was directly copied; API patterns were adapted for the auction use case.

Stigmerge~\cite{stigmerge2024}, a Veilid-based file-sharing application, was studied for its use of \texttt{app\_call} over private routes for reliable message delivery. The delivery pattern was adapted for the MPC tunnel proxy; Stigmerge's DHT-write approach was not used.
