% Chapter 2: Output Summary — Handbook 8.2.3
% Maximum 2 PAGES.

\section{Output Summary}
\label{sec:output-summary}

Table~\ref{tab:outputs} summarises the project deliverables.

\begin{table}[H]
\centering
\small
\renewcommand{\arraystretch}{1.3}
\makebox[\textwidth][c]{%
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Output} & \textbf{Type / Size} & \textbf{Recipient} & \textbf{Report reference} \\
\hline
Lattice application & Rust crate, ${\sim}$15k lines & Consultant, Veilid community & Sections~\ref{sec:results-architecture}--\ref{sec:results-testing} \\
\hline
\texttt{auction\_n.mpc} & MP-SPDZ DSL, 46 lines & Consultant & Section~\ref{sec:results-mpc} \\
\hline
Benchmark harness & Rust binary + 354 trials (CSV) & Consultant & Section~\ref{sec:results-benchmarks} \\
\hline
Devnet tooling & Makefile, playground orchestrator & Consultant, Veilid community & Section~\ref{sec:method-approach} \\
\hline
Demo video & 15-min narrated recording & Examiners & \textit{Submitted separately} \\
\hline
This report & LaTeX source in repo & Examiners & --- \\
\hline
\end{tabular}}%
\caption{Project deliverables.}
\label{tab:outputs}
\end{table}

The Lattice application was a desktop program built with Dioxus~0.7.2 that
embedded a Veilid node, provided a graphical interface for creating listings
and placing bids, and orchestrated the full MPC-based winner-determination
flow.  A headless binary (\texttt{market-headless}) was created to reduce the
friction of automated end-to-end testing without the overhead of running a GUI. 
The MPC protocol was drop-in: the auction
program compiled against any MP-SPDZ backend, and the runtime protocol was
selected via an environment variable.  MASCOT and Shamir were benchmarked,
but any MP-SPDZ protocol supporting $N$-party computation could be substituted
without code changes.

The benchmark harness (\texttt{bench-auction}) automated multi-party auction
trials across configurable party counts (3--20) and devnet sizes (40, 60, 80
nodes), collecting wall-clock time, MPC computation time, route-exchange
latency, tunnel bandwidth, and success rates.

\subsection*{Reuse Summary}

The application depended on Veilid (MPL-2.0) for networking, MP-SPDZ
(BSD-3-Clause) for MPC execution, and Dioxus (MIT/Apache-2.0) for the
desktop UI.  No code was directly copied from reference applications; the
\texttt{app\_call} delivery pattern over private routes was adapted from
Stigmerge~\cite{stigmerge2024}, a Veilid-based file-sharing application.
A detailed component-level reuse table is provided in Appendix~\ref{app:reuse}.

All source code, build scripts, benchmark data, and this report are available
in the project repository at
\url{https://github.com/anker-rasmussen/Dissertation} (including submodules).
The Rust crate was not published on crates.io or any public registry; it is
available only as source code in the repository.
