% Chapter 4: Method — Handbook 8.2.5
% ~2500 words

\section{Method}
\label{sec:method}

\subsection{Development Approach}
\label{sec:method-approach}

Development followed an iterative, milestone-driven plan defined in the PDD
(Appendix~\ref{app:pdd}).  The foundation phase (Nov--Dec~2025) focused on
understanding the Veilid API, establishing a development
environment as well as modifying a draft merge request \cite{veilid-devnet-mr444} to fit my usecase
(creating hooking a socket library using LD\_PRELOAD), and scaffolding the application.  Milestone~1 (Jan--Feb~2026)
delivered listing and bidding flows over the DHT.  Milestone~2 (Feb--Mar~2026)
integrated real MPC via MP-SPDZ, culminating in three passing end-to-end tests.
Milestone~3 (late Mar~2026) focused on benchmarking, the protocol comparison,
and this report.

The original plan included a fourth milestone for Monero testnet settlement;
this was descoped to prioritise MPC tunnel reliability and the MASCOT vs.\
Shamir comparison, which proved more technically demanding and more
academically interesting than payment integration.

\subsubsection{Infrastructure}

As discussed in Section~\ref{sec:ctx-veilid-bootstrap}, Veilid requires each
node to have a unique public IP address.  Developing against the public Veilid
network was impractical: misconfigured nodes sharing an IP address trigger an
hour-long ban on that IP, during which no Veilid node can bootstrap from
it~\cite{rioux2026_ip_punishment}.  A private devnet avoids this penalty and
allows rapid iteration.  The devnet satisfies the unique-IP constraint using
two approaches:

The playground devnet launched Veilid processes directly on the host, each
assigned a unique IP via \texttt{libipspoof.so}, which intercepted socket
calls to map fake public addresses (\texttt{1.2.3.1}--\texttt{1.2.3.255})
to localhost,supporting up to 255 nodes on a single machine.  The
bootstrap node at \texttt{1.2.3.1:5150} was configured following the
official Veilid bootstrap guide~\cite{veilid_bootstrap_setup}.  Lattice nodes took the earliest unused offset above the devnet range,
allowing the same addressing scheme to scale across the 40-, 60-, and
80-node devnets used in benchmarking.

Figure~\ref{fig:devnet-topology} shows the devnet layout.

\begin{figure}[htbp]
  \centering
  \begin{tikzpicture}[
    node/.style={draw, circle, minimum size=0.7cm, font=\scriptsize,
                 inner sep=0pt, thick},
    bstrap/.style={node, double, double distance=1pt},
    market/.style={node, fill=black!8},
    lbl/.style={font=\scriptsize},
    conn/.style={thin},
  ]
  % 5 devnet nodes in a pentagon
  \node[bstrap] (d0) at (90:2cm)  {0};
  \node[node]   (d1) at (162:2cm) {1};
  \node[node]   (d2) at (234:2cm) {2};
  \node[node]   (d3) at (306:2cm) {3};
  \node[node]   (d4) at (18:2cm)  {4};

  % Full mesh (each node connected to every other)
  \draw[conn] (d0) -- (d1);
  \draw[conn] (d0) -- (d2);
  \draw[conn] (d0) -- (d3);
  \draw[conn] (d0) -- (d4);
  \draw[conn] (d1) -- (d2);
  \draw[conn] (d1) -- (d3);
  \draw[conn] (d1) -- (d4);
  \draw[conn] (d2) -- (d3);
  \draw[conn] (d2) -- (d4);
  \draw[conn] (d3) -- (d4);

  % 3 Lattice market nodes in a dashed box
  \node[node] (m20) at (5.0, 1.2)  {20};
  \node[node] (m21) at (5.0, 0.0)  {21};
  \node[node] (m22) at (5.0,-1.2)  {22};

  \node[draw, dashed, rounded corners=6pt, inner sep=10pt,
        fit=(m20)(m21)(m22),
        label={[lbl]above:Lattice (application)}] {};

  % Market nodes mesh with devnet + each other
  \draw[conn] (m20) -- (d0);
  \draw[conn] (m20) -- (d4);
  \draw[conn] (m21) -- (d4);
  \draw[conn] (m21) -- (d3);
  \draw[conn] (m22) -- (d3);
  \draw[conn] (m22) -- (d2);
  \draw[conn] (m20) -- (m21);
  \draw[conn] (m21) -- (m22);

  % Labels
  \node[lbl, anchor=south] at ([yshift=3pt]d0.north) {bootstrap};
  \node[lbl] at (0, -3) {Devnet (5 of 20--80 shown)};
  \node[lbl, align=left] at (7.8, 0)
    {IP: \texttt{1.2.3.($n$+1)}\\
     Port: \texttt{5150+$n$}\\[2pt]
     All on one machine\\
     via \texttt{libipspoof.so}};
  \end{tikzpicture}
  \caption{Playground devnet topology (subset shown).  Node~0 (double
    border) is the bootstrap server; after initial discovery all nodes
    form a P2P mesh.  Lattice market nodes (shaded) join with offsets
    above the devnet range.  All nodes run on a single machine with
    \texttt{LD\_PRELOAD} IP spoofing.}
  \label{fig:devnet-topology}
\end{figure}

The devnet was automated via Makefile targets.  \texttt{make demo} built
everything from source, started the devnet, and launched a three-node auction
with no manual setup.  Benchmark runs (Section~\ref{sec:results-benchmarks})
used devnets of 40, 60, and 80 nodes to evaluate how network size affected
route stability and auction success rates.

\subsection{Architecture}
\label{sec:method-architecture}

\subsubsection{Auction State Machine}
\label{sec:method-state-machine}

Auction logic was abstracted behind traits (\texttt{DhtStore},
\texttt{RandomSource}) so that the full lifecycle could be tested with mock
implementations.  Each auction progressed through six phases
(Figure~\ref{fig:auction-fsm}).  Phase transitions are driven by events:
the deadline timer, DHT reads completing, \texttt{app\_call} responses
arriving, and the MP-SPDZ process exiting.

\begin{figure}[htbp]
  \centering
  \begin{tikzpicture}[
    proc/.style={draw, minimum width=2.8cm, minimum height=0.8cm,
                 font=\small, align=center},
    decision/.style={draw, diamond, aspect=2.2, inner sep=1pt,
                     font=\scriptsize, align=center},
    term/.style={draw, rounded corners=8pt, minimum width=2.2cm,
                 minimum height=0.7cm, font=\small},
    trans/.style={-{Stealth}, thick},
    lbl/.style={font=\scriptsize, fill=white, inner sep=1pt},
    node distance=1.1cm,
  ]
  % Terminals and processes
  \node[term] (start) {Active};
  \node[proc, below=of start] (collect) {Collect\\[-2pt]Routes};
  \node[decision, below=1.3cm of collect] (droutes) {All routes\\collected?};
  \node[proc, below=1.3cm of droutes] (barrier) {Readiness\\[-2pt]Barrier};
  \node[decision, below=1.3cm of barrier] (dready) {All acks\\received?};
  \node[proc, below=1.3cm of dready] (mpc) {MPC\\[-2pt]Execution};
  \node[decision, below=1.3cm of mpc] (dmpc) {MPC\\succeeded?};
  \node[proc, below=1.3cm of dmpc] (verify) {Verify \&\\[-2pt]Deliver Key};
  \node[term, below=of verify] (done) {Completed};
  \node[term, right=2.8cm of done] (fail) {Failed};

  % Happy path
  \draw[trans] (start) -- node[lbl, right] {deadline expires} (collect);
  \draw[trans] (collect) -- (droutes);
  \draw[trans] (droutes) -- node[lbl, right] {yes} (barrier);
  \draw[trans] (barrier) -- (dready);
  \draw[trans] (dready) -- node[lbl, right] {yes} (mpc);
  \draw[trans] (mpc) -- (dmpc);
  \draw[trans] (dmpc) -- node[lbl, right] {yes} (verify);
  \draw[trans] (verify) -- (done);

  % Retry loops
  \draw[trans] (droutes.west) -- node[lbl, above] {no} ++(-1.6,0)
    |- (collect.west);
  \draw[trans] (dready.west) -- node[lbl, above] {no} ++(-1.6,0)
    |- (barrier.west);

  % Failure paths
  \draw[trans] (dmpc.east) -- node[lbl, above] {no} ++(1.4,0)
    |- (fail.west);

  \end{tikzpicture}
  \caption{Auction phase flowchart.  Rectangles are processing phases;
    diamonds are decision points; rounded boxes are terminal states.
    The ``no'' paths from route collection and readiness barrier represent
    retry loops (DHT re-poll and route refresh respectively).
    MPC failure leads to the Failed terminal.  Each participant independently
    tracks this flow for every auction.}
  \label{fig:auction-fsm}
\end{figure}

\subsubsection{DHT Record Hierarchy}
\label{sec:method-dht-hierarchy}

All marketplace state was stored in Veilid's DHT.
Figure~\ref{fig:dht-hierarchy} shows the record hierarchy.
Each MPC party published its route blob to its bid's DHT record
(subkey~1), the \emph{route-in-DHT} pattern adapted from
Stigmerge~\cite{stigmerge2024}.  This aligns with the DHT shared-writer
pattern recommended by the Veilid lead
developer~\cite{rioux2025_dht_patterns}; Veilid~0.6.0 is expected to
automate this via DHT route autopublish.
\label{sec:method-mpc}

\begin{figure}[htbp]
  \centering
  \begin{tikzpicture}[
    rec/.style={draw, minimum width=2.1cm, minimum height=0.9cm,
                font=\small, align=center, thick},
    sk/.style={draw, dashed, minimum width=2.2cm, minimum height=0.6cm,
               font=\scriptsize, align=center},
    actor/.style={draw, circle, minimum size=0.7cm, font=\scriptsize,
                  inner sep=0pt, thick, fill=blue!10},
    arr/.style={-{Stealth[length=2.5mm]}, thick},
    warr/.style={-{Stealth[length=2.5mm]}, thick, dashed, blue!60},
    lbl/.style={font=\scriptsize, midway, fill=white, inner sep=1pt}
  ]
    % Master registry
    \node[rec, fill=gray!15] (reg) at (0,0) {Market\\Registry};

    % Seller catalogs
    \node[rec, fill=gray!15] (s1) at (-3,-2) {Seller\\Catalog};
    \node[rec, fill=gray!15] (s2) at (3,-2) {Seller\\Catalog};

    \draw[arr] (reg) -- (s1);
    \draw[arr] (reg) -- (s2);

    % Listings
    \node[rec] (l1) at (-4.5,-4.2) {Listing};
    \node[rec] (l2) at (-1.5,-4.2) {Listing};
    \node[rec] (l3) at (3,-4.2) {Listing};

    \draw[arr] (s1) -- (l1);
    \draw[arr] (s1) -- (l2);
    \draw[arr] (s2) -- (l3);

    % Listing subkeys
    \node[sk] (l1s0) at (-5.8,-5.8) {SK\,0: Data};
    \node[sk] (l1s1) at (-3.2,-5.8) {SK\,1: G-Set\\(Bid Announce.)};
    \draw[arr, thin] (l1) -- (l1s0);
    \draw[arr, thin] (l1) -- (l1s1);

    % Bidders writing to G-Set
    \node[actor] (bidA) at (-5.5,-7.2) {$B_1$};
    \node[actor] (bidB) at (-3.2,-7.2) {$B_2$};
    \node[font=\scriptsize] at (-1.7,-7.2) {$\cdots$};
    \node[actor] (bidN) at (-0.9,-7.2) {$B_n$};

    \draw[warr] (bidA) -- (l1s1);
    \draw[warr] (bidB) -- (l1s1);
    \draw[warr] (bidN) -- (l1s1);

    % Bid records
    \node[rec] (b1) at (-5.5,-8.8) {Bid};
    \node[rec] (b2) at (-3.2,-8.8) {Bid};
    \node[font=\scriptsize] at (-1.7,-8.8) {$\cdots$};
    \node[rec] (bn) at (-0.9,-8.8) {Bid};

    \draw[arr, thin] (bidA) -- (b1);
    \draw[arr, thin] (bidB) -- (b2);
    \draw[arr, thin] (bidN) -- (bn);

    % Bid subkeys (show for b1 only)
    \node[sk] (b1s0) at (-7.2,-10.2) {SK\,0: Bid\\Record};
    \node[sk] (b1s1) at (-4.2,-10.2) {SK\,1: MPC\\Route Blob};
    \draw[arr, thin] (b1) -- (b1s0);
    \draw[arr, thin] (b1) -- (b1s1);

    \node[font=\scriptsize, gray] at (-0.9,-9.8) {\textit{(same layout)}};
  \end{tikzpicture}
  \caption{DHT record hierarchy.  Shaded boxes are directory records;
    dashed boxes show subkey layout.  Bidders ($B_1$--$B_n$, dashed arrows)
    each merge their announcement into the listing's G-Set CRDT
    (subkey~1) and own an individual bid record.  Each node also
    maintains a local copy of the G-Set in memory; periodic DHT reads
    merge remote state into the local copy, ensuring convergence.
    Each bid record's subkey~1 carries the MPC route blob for
    DHT-backed route exchange.}
  \label{fig:dht-hierarchy}
\end{figure}

\newpage
\subsubsection{MPC Tunnel}
MP-SPDZ processes communicate via TCP.  On a direct network this is trivial;
over Veilid, each TCP connection must be tunnelled through onion-routed private
routes.  The \texttt{MpcTunnelProxy} module bridged the two worlds:

\begin{enumerate}
  \item The MPC orchestrator collects route blobs from all parties via DHT
    reads (with \texttt{app\_message} announcement as a fast path and DHT
    polling as a reliable fallback).
  \item A local TCP listener accepts connections from the MP-SPDZ process and
    forwards each send as a Veilid \texttt{app\_call} to the target party's
    private route.  The receiver's \texttt{app\_call} handler feeds the
    payload into a local TCP connection to its own MP-SPDZ process.
  \item Sends are pipelined with a bounded semaphore (depth~8) to overlap
    network round trips.  A per-stream reorder buffer handled out-of-order
    delivery.
\end{enumerate}

All point-to-point MPC traffic used \texttt{app\_call} (SYN/ACK)
rather than \texttt{app\_message} (fire-and-forget), following the pattern
established by Stigmerge~\cite{stigmerge2024}.  This ensures failed deliveries
are detected immediately, a critical requirement for MPC, where a single
lost message causes the protocol to hang.

\subsubsection{Winner Verification and Content Delivery}
\label{sec:method-verification}

After MPC completes, the seller (party~0) knows the winner's identity and
winning bid value.  Content delivery used a commitment-and-challenge scheme:

\begin{enumerate}
  \item The seller sends a challenge to the claimed winner via
    \texttt{app\_call} over their MPC route.
  \item The winner responds with their bid value and nonce, proving knowledge
    of the committed bid.
  \item The seller verifies the commitment
    $C = \text{SHA-256}(\mathit{bid} \| \mathit{nonce})$ matches the on-DHT
    record, then sends the AES-256-GCM decryption key.
\end{enumerate}

The PDD originally proposed 1-out-of-$N$ oblivious transfer for this step.
The implemented scheme is simpler: because the seller already learns the
winning bid as MPC party~0, OT would add complexity without additional privacy
benefit.  The commitment scheme ensures the seller cannot substitute a
different winner, and the \texttt{app\_call} delivery ensures the key transfer
is confirmed.

\subsection{Technology Choices}
\label{sec:method-tech}

\subsubsection{Why Veilid}

Veilid provides keyed endpoints, a secure DHT, and private routing in a
single embeddable library (Table~\ref{tab:overlay-comparison}).  Each auction
participant runs a full Veilid node in-process, avoiding the external daemon
or SOCKS proxy required by Tor or I2P.

\subsubsection{Why MP-SPDZ}

MP-SPDZ~\cite{mp-spdz} was selected for MPC execution because it supports
multiple protocol backends from a single high-level program, enabling the
MASCOT vs.\ Shamir comparison central to the evaluation.  The framework is
actively maintained, well-documented, and provides the
\texttt{mascot-party.x} and \texttt{shamir-party.x} binaries used in
benchmarking.

\subsubsection{Why MASCOT and Shamir}

These two protocols represent opposite ends of the MPC trust spectrum:

\begin{itemize}[noitemsep]
  \item \textbf{MASCOT} (dishonest majority, malicious security): tolerates
    up to $N{-}1$ corrupt parties.  Suitable for an untrusted P2P setting
    where any participant might be adversarial.  The cost is $O(N^2)$
    bandwidth from pairwise OT.
  \item \textbf{Shamir} (honest majority, semi-honest security): requires
    $< N/2$ corrupt parties.  Much lower communication overhead (linear in
    $N$), but the assumption may not hold in an open marketplace.
\end{itemize}

Replicated secret sharing (3-party, honest majority) was used during early
development as the simplest protocol to validate the integration pipeline.  It
is not included in the benchmark comparison because it is fixed to exactly
three parties, making scaling analysis impossible.

Other MP-SPDZ backends (semi-honest two-party, BMR garbled circuits,
SPDZ2k over rings) were not tested because they either do not support
arbitrary $N$, target a different threat model, or solve the same trust
assumption as one of the two selected protocols.  MASCOT and Shamir were chosen
to isolate the single most impactful variable: honest vs.\ dishonest majority.

\subsubsection{Serialisation Strategy}

Two serialisation formats are used:
\begin{itemize}[noitemsep]
  \item \textbf{CBOR} for DHT-stored records (listings, bids, route entries).
    CBOR is self-describing and tolerates schema evolution, important for
    data that persists in Veilid's DHT (32\,KB value limit).
  \item \textbf{Bincode} for ephemeral wire messages
    (\texttt{AuctionMessage} enum via \texttt{app\_call}).  More compact than
    CBOR but brittle across schema changes, acceptable for messages that are
    never stored.
\end{itemize}

\subsubsection{UI Framework}

Dioxus~0.7.2 provides a React-like desktop UI with a GTK/WebKit backend.
The UI was not a focus of the project; it served as a thin presentation layer
over the auction logic.  A headless binary (\texttt{market-headless}) was
built for E2E testing, bypassing the UI entirely.

\subsection{Testing Strategy}
\label{sec:method-testing}

Testing followed a three-tier approach:

\begin{enumerate}
  \item \textbf{Unit tests} (${\sim}$169 tests): in \texttt{src/} alongside
    modules.  Fast, isolated, no network dependencies.
  \item \textbf{Integration tests} (${\sim}$63 tests): in \texttt{tests/}.
    Use mock DHT, mock time, and mock randomness to simulate full $N$-party
    auction flows.  A \texttt{MultiPartyHarness} sets up $N$ independent
    \texttt{AuctionLogic} instances sharing a \texttt{MockDht} backend,
    enabling deterministic testing of bid ordering, ties, edge cases, and
    MPC output parsing.  All integration tests complete in under one second.
  \item \textbf{End-to-end tests} (3~tests): in \texttt{tests/e2e/}.  Run
    against the playground devnet with \texttt{LD\_PRELOAD} IP spoofing.  Each
    test launches separate OS processes (\texttt{market-headless}) and
    exercises the full Veilid networking stack.  These tests run sequentially
    (\texttt{-{}-test-threads=1}) because they share Veilid infrastructure.
\end{enumerate}

The three E2E tests cover:
\begin{itemize}[noitemsep]
  \item \textbf{Happy path}: single auction, 3~parties, listing
    $\rightarrow$ bids $\rightarrow$ MPC $\rightarrow$ verification
    $\rightarrow$ decryption key delivery.
  \item \textbf{Sequential auctions}: two auctions in sequence on the same
    nodes, testing route refresh between sessions.
  \item \textbf{Concurrent auctions}: two auctions with overlapping timelines,
    testing the constraint that only one MPC session can be active per node
    (due to Veilid's single-active-route limitation).
\end{itemize}

\subsection{Reuse and Attribution}
\label{sec:method-reuse}

The project built on three major external components:
\begin{itemize}[noitemsep]
  \item \textbf{Veilid} (MPL-2.0): P2P networking, DHT, private routing.
    Used as a library dependency; no modifications to Veilid source were
    required for the Lattice application.
  \item \textbf{MP-SPDZ} (BSD-3-Clause): MPC protocol execution.  The
    46-line \texttt{auction\_n.mpc} program is original; the framework
    binaries are used unmodified.
\end{itemize}

The \texttt{app\_call} delivery model and route-in-DHT pattern were informed
by Stigmerge~\cite{stigmerge2024}, a Veilid file-sharing application; no code
was copied.  A full component-level reuse table is provided in
Appendix~\ref{app:reuse}.
